Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-05 paper/galsize_paper.tex
Added flesh to 5.1

The contrast between the two bottom panels is stark. The clustering of large vs. small bulge-dominated galaxies has almost no dependence upon $\rhalf.$ On the other hand, for disk-dominated galaxies, small galaxies are much more strongly clustered, and the effect is strong. In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples. We discuss a halo model interpretation of these trends in \S\ref{sec:future}.

@@

In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass. First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered. So in models where satellites are smaller than centrals, at fixed $\mstar$ the ``small" subsample will naturally have a higher satellite fraction, boosting the clustering of small galaxies relative to large of the same stellar mass. Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}. Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered. We highlight this point in section \ref{subsec:mstar_stripping} below by testing predictions for satellite mass loss models that do not possess central vs. satellite size differences.

{\color{blue} Important point/sentence to reincorporate here, after deleting from above:} Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds. {\color{blue} The analogous point should be made when discussing the role of color/morphology selection}.

>>>>

The contrast between the two bottom panels is stark. The clustering of large vs. small bulge-dominated galaxies has almost no dependence upon $\rhalf.$ On the other hand, for disk-dominated galaxies, small galaxies are much more strongly clustered, and the effect is strong. In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples. We discuss a halo model interpretation of these trends in \S\ref{sec:interpretation}.

@@

In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass. First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered. So in models where satellites are smaller than centrals, at fixed $\mstar$ the ``small" subsample will naturally have a higher satellite fraction, boosting the clustering of small galaxies relative to large of the same stellar mass. Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}. Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.

We can also understand the $\mstar-$dependence of Figure \ref{fig:clustering_ratio_upshot} in term of the relative sizes of centrals vs. satellites. The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}. As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies. Thus models where $\rhalf-$dependent clustering is driven by satellite vs. central size naturally predict the observed $\mstar-$dependence of the signal, without introducing any explicitly $\mstar-$dependent ingredients in the size model.

Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since trends dramatically weaken and change sign. However, even very simple models based entirely on central vs. satellite size differences can give rise to this behavior.

{\color{blue} APH: finish discussion of color and morphology.}
